\section{Cobb-Douglas production} \label{sec:intro}

In this assignment we want to test whether the Cobb-Douglas production function (CD) exhibits constant returns to scale (CRS) at a firm level using real data and panel data methods. The Cobb-Douglas production function is given by,
\begin{align} \label{eq:CD}
    F(K,L) = A K^{\beta_K} L^{\beta_L}
\end{align}
where $K$ is capital, $L$ is labor, $A$ is total factor productivity (TFP) and $\beta_K, \beta_L$ are the output elasticities of capital and labor, respectively.
It follows that for CD to have CRS, it must be homogeneous of degree one, i.e. $\beta_K + \beta_L = 1$, as seen from,
\begin{align*} 
    F(\lambda K, \lambda L) &= A (\lambda K)^{\beta_K} (\lambda L)^{\beta_L} = A \lambda^{\beta_K + \beta_L} K^{\beta_K} L^{\beta_L} = \lambda F(K,L) \iff \beta_K + \beta_L = 1.
\end{align*} 
which forms the linear hypothesis we want to test i.e. $H_0: \beta_K + \beta_L = 1$ vs. $H_A: \beta_K + \beta_L \neq 1$.
While $K$ and $L$ are certainly important production inputs, we cannot hope to observe \textbf{all} input factors that make up production. To investigate the functional form of the production function, we estimate a simple (two-way) fixed effects (FE) model, to remove the time-invarying and time-varying unobserved heterogeneity. Note, that these factors with control for much more than just TFP, in fact all other unobserved factors that affect production. 

% We start by taking logs of the production function to linearize it,
% \begin{align*}
%     \ln Y_{it} &= \ln A_{it} + \beta_K \ln K_{it} + \beta_L \ln L_{it} \\
%     y_{it} &= \beta_K k_{it} + \beta_L l_{it} + u_{it}, \quad u_{it} = \ln A_{it}
% \end{align*}
% Suppose that $\ln A_{it}$ can be decomposed into time-invariant firm-specific effects, $\alpha_i$, a time-varying effects, $\gamma_t$, and add an idiosyncratic error, $\varepsilon_{it}$, i.e. $u_{it} = \alpha_i + \gamma_t + \varepsilon_{it}$. The FE model is then given by,
% \begin{align*}
%     u_{it} &= \alpha_i + \gamma_t + \varepsilon_{it}, \\
%     y_{it} &= \alpha_i + \gamma_t + \beta_K k_{it} + \beta_L l_{it} + \varepsilon_{it},
% \end{align*} 
% where $y_{it} = \ln Y_{it}$, $k_{it} = \ln K_{it}$ and $l_{it} = \ln L_{it}$. Collect the RHS variables in the vector $\bm{x}_{it} = (k_{it}, l_{it})$ and the parameters in the vector $\bm{\beta} = (\beta_K, \beta_L)$. The FE model can then be written on compact form as,
% \begin{align*}
%     y_{it} = \alpha_i + \gamma_t + \bm{x}_{it} \bm{\beta} + \varepsilon_{it}.
% \end{align*}

% Due to $\alpha_i$ and $\gamma_t$ being unobserved, we cannot estimate them directly, and if we suspect that they are correlated with $\bm{x}_{it}$, we need to control for them to obtain consistent estimates of the parameters. This can be done by transforming the data to remove these effects, and then estimate the parameters using OLS on the transformed data.

% The transformation used to remove $\alpha_i$ is the within transformation, which subtracts the individual specific mean from each observation, i.e. $\tilde{y}_{it} = y_{it} - \bar{y}_i$, where $\bar{y}_i = \frac{1}{T} \sum_{t=1}^T y_{it}$ is the individual specific mean. Similarly to remove the time variant fixed effect, we can use the time within transformation, which subtracts the time specific mean from each observation, i.e. $\dot{y}_{it} = y_{it} - \bar{y}_t$, where $\bar{y}_t = \frac{1}{N} \sum_{i=1}^N y_{it}$ is the time specific mean. However, since we have both individual and time fixed effects, we need to use a two-way transformation to remove both effects. This can be done by applying the within transformation twice, first over the individual dimension and then over the time dimension (or vice versa). 

% Denote the transformation matrices, 
% \begin{align*}
%     Q_T = I_T - \frac{1}{T} \iota_T \iota_T', \quad Q_N = I_N - \frac{1}{N} \iota_N \iota_N',
% \end{align*}

% The same transformation is applied to $\bm{x}_{it}$ and $\varepsilon_{it}$, i.e. $\tilde{\bm{x}}_{it} = \bm{x}_{it} - \bar{\bm{x}}_i$ and $\tilde{\varepsilon}_{it} = \varepsilon_{it} - \bar{\varepsilon}_i$. The time fixed effects, $\gamma_t$, can be removed by including time dummies in the regression (or by a similar transformation over the cross-sectional dimension). The transformed model is then given by, 
% \begin{align*}
%     \tilde{y}_{it} = \tilde{\bm{x}}_{it} \bm{\beta} + \tilde{\varepsilon}_{it}.
% \end{align*}


\textbf{Gameplan:}

Write stuff about assumptions, and then transformations, prob go from inconsistent pooled OLS to consistent FE. Right the estimator, list assumptions for identification and consistency (strict/cont exog, non-degeneracy) -> show consistency by LLN convergence in plim. Next, talk about asymptotic normality, CLT, variance estimation (efficiency - robust, cluster). Finally, hypothesis testing (Wald). Then proceed to empirical application (include wald-test code, since it is not given or done in any exercises). 

\begin{itemize}
    \item Mikkel: Requirements for FE and why pooled OLS is inconsistent (identification, assumptions, consistency, exogeneity). 
    \item Mikkel: Show consistency (LLN $\to$ plim convergence). 
    \item Mikkel: Show Asymptotic normality.
    \item Mathias: Show Efficiency (Robust or not).
    \item Noah: Seriel Corr, Rank test, Homoskedasticity (maybe). 
    \item Noah: Wald-Test (one sided as well)? Check form of test when using robust std. err. 
    \item Mathias: Potentially the above, for time variant fixed effects.
    \item Noah: Present empirical results. 
    \item Noah: Estimation table. 
    \item Noah: Misspecification test table.
    \item Noah: Test table for linear hypothesis (Wald). 
    \item Få styr på fejlled, u, v, vareps?
    \item Missing references for eq's 
    \item assignment structure i.e. numbered headers, order of secs/subsecs/subsubsecs?
\end{itemize}

Plan:
\begin{enumerate}
    \item Alle prøver at nå at lave hver deres til/inden torsdag
    \item Alle læser hinandens arbejde torsdag eftermiddag
    \item Zoom møde fredag eftermidag, hvor vi får den sendt afsted
\end{enumerate}